\LARGE TN1008 \\ Advanced Simulation and Visualization of Fluids in Computer Graphics \\ \Large Divergence-Free Smoothed Particle Hydrodynamics

### 2016-12-05 report/paper.tex
Put in some code

@@

\section{Method}
%What have you done?
%How did you do it?
%Why did you do it that way?
%May want to mention why you *didn’t* do it in some 
%other possible way
%Clear enough that you could hand the report to another student and they could reproduce the work!
%Probably no need to mention programming language etc
\subsection{Neighbourhood search}
    Since SPH only considers a finite amount of neighbouring particles, it is important to keep track of every particles neighbours.
    Searching through all particles for neighbours within the cutoff distance $H$ for every particle is inefficient and takes $\mathcal{O}({N^2})$ time.
    The cutoff distance $H$ is the kernel smoothing radius.
    To fasten this up a cell list was implemented.
    A cell list is a data structure that is divided into cells that have a length larger or equals to the cutoff distance $H$.
    When finding the neighbour of particle $i$, only the neighbouring cells have to be searched for particles within the cutoff distance, see figure~\ref{fig:cellList}.

@@

    The cell list is implemented by using a four dimensional vector where the first three dimensions are for the x, y and z coordinates for the cells and the fourth dimension is for storing the particles belonging to the cell.
    The amount of cells are decided by dividing the scene into cells of length $H$.
    The particles are then assigned to a cell.
    If the particle moves out of its cell it is then assigned to the new cell.

    \begin{equation} \label{eq:assignCell}

    \end{equation}

>>>>

% Our packages
\usepackage{listings} % To write code in latex
\usepackage{color}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2,
    literate={\ \ }{{\ }}1
}

\lstset{style=mystyle}

@@

\section{Method}
%What have you done?
%How did you do it?
%Why did you do it that way?
%May want to mention why you *didn’t* do it in some 
%other possible way
%Clear enough that you could hand the report to another student and they could reproduce the work!
%Probably no need to mention programming language etc

\begin{lstlisting}[language=C++, mathescape=true, escapeinside={(*}{*)}]
function performSimulation
    for all particles $i$ do //Init neighbourhoods
        find neighbourhoods $N_i(0)$
    for all particles $i$ do //Init $\color{codegreen}\rho_i$ and $\color{codegreen}\alpha_i$
        compute densities $\rho_i(0)$
        compute factors $\alpha_i(0)$
    while (t < $t_{max}$) do //Start simulation loop
        adapt time step $\Delta{t}$ 
        for all particles $i$ do //Predict velocities $\color{codegreen}\mathbf{v}_i^*$
            $\mathbf{v}_i = \mathbf{v}_i + \Delta{t}\mathbf{F}_i^{adv}/m_i$
        correctDensityError($\alpha, \mathbf{v}_i$) //Fulfill $\color{codegreen}\rho^* - \rho_0 = 0$
        for all particles $i$ do //Update positions
            $x_i(t + \Delta{t}) = x_i(t) + \Delta{t}\mathbf{v}_i^*$
        for all particles $i$ do //Update neighbourhoods
            find neighbourhoods $N_i(t + \Delta{t})$
        for all particles $i$ do //Update $\color{codegreen}\rho_i$ and $\color{codegreen}\alpha_i$ 
            compute densities $\rho_i(0)$
            compute factors $\alpha_i(0)$
        correctDivergenceError($\alpha, \mathbf{v}^*$) //Fulfill $\color{codegreen}\frac{D\rho}{Dt} = 0$

\end{lstlisting}

\subsection{Neighbourhood search}
    Since SPH only considers a finite amount of neighbouring particles, it is important to keep track of every particles neighbours.
    Searching through all particles for neighbours within the cutoff distance $H$ for every particle is inefficient and takes $\mathcal{O}({N^2})$ time.
    The cutoff distance $H$ is the kernel smoothing radius.
    To fasten this up a cell list was implemented.
    A cell list is a data structure that is divided into cells that have a length larger or equals to the cutoff distance $H$.
    When finding the neighbour of particle $i$, only the neighbouring cells have to be searched for particles within the cutoff distance, see figure~\ref{fig:cellList}.

@@

    The cell list is implemented by using a four dimensional vector where the first three dimensions are for the x, y and z coordinates for the cells and the fourth dimension is for storing the particles belonging to the cell.
    The amount of cells are decided by dividing the scene into cells of length $H$.
    The particles are then assigned to a cell according to equation~ref{eq:assignCell}.
    If the particle moves out of its cell it is then assigned to the new cell.

    \begin{equation} \label{eq:assignCell}
        sjdfkljsf
    \end{equation}
